Soling at the 2000 Summer Olympics

### 2020-07-26 inst/f1points.Rmd
bugfix, should *not* save!
typo

Thus, for 2017 at least, we see that the current poionts system agrees
with likelihood ranking for the top four places, while Zipf's law
agrees to three.

@@

```{r,label=definemultiplemontecarlo, echo=FALSE}
load("formula1_results_2017.rda") # this created by running f1points_Omaker.R; file contains R variables OO and pointslist
```

@@

```{r,label=somesummaries}
summarytable <- data.frame(
means = apply(OO,1,mean),
winner_correct = rowSums(OO>1),
all_correct = rowSums(OO==top))
rownames(summarytable) <- names(pointslist)
summarytable
```

```{r,fig=TRUE}
typecol <- c(rep("red",2),rep("orange",10),rep("blue",11),rep("orange",1),rep("black",7),rep("gray",7))
plot(summarytable[,1],ylab='mean',pch=16,col=typecol)
plot(summarytable[,2],ylab='prob of winner correct',pch=16,col=typecol)
plot(summarytable[,3],ylab='prob. of total rank order correct',pch=16,col=typecol)
```

and visual:

```{r,label=plotcumulativeM,fig=TRUE}
o <- t(apply(1+OO,1,tabulate))
#matplot(0:11,apply(o[,12:1],1,cumsum)/1e3,type='b',lty=1,pch=16,ylab='probability',axes=FALSE,xlab='number incorrect')
jj <- c(0,2,4,6,8,11)
#axis(1,pos=0,at=jj,labels=c("0",paste("<=",jj[-1],sep="")))
#axis(2)
```

```{r,makeatable}
table(real_winner_ok=OO[1,]>0,top3_winner_ok=OO[3,]>0)
save(OO,file="~/rstudio/hyper2/inst/cache_results_2017.Rd")
```

>>>>

Thus, for 2017 at least, we see that the current points system agrees
with likelihood ranking for the top four places, while Zipf's law
agrees to three.

@@

```{r,label=definemultiplemontecarlo, echo=FALSE}
load("formula1_results_2016.rda") # this created by running f1points_Omaker.R; file contains R variables OO and pointslist
OO2016 <- OO

load("formula1_results_2017.rda") # this created by running f1points_Omaker.R; file contains R variables OO and pointslist
OO2017 <- OO

load("formula1_results_2018.rda") # this created by running f1points_Omaker.R; file contains R variables OO and pointslist
OO2018 <- OO

load("formula1_results_2019.rda") # this created by running f1points_Omaker.R; file contains R variables OO and pointslist
OO2019 <- OO
```

@@

```{r,label=somesummaries}
summarytablemaker <- function(OO){
  out <- data.frame(
      means = apply(OO,1,mean),
      winner_correct = rowSums(OO>1)/ncol(OO),
      all_correct = rowSums(OO==top)/ncol(OO)
  )
  rownames(out) <- names(pointslist)
  return(out)
}
s2016 <- summarytablemaker(OO2016)
s2017 <- summarytablemaker(OO2017)
s2018 <- summarytablemaker(OO2018)
s2019 <- summarytablemaker(OO2019)
```

```{r,fig=TRUE}
typecol <- c(rep("red",2),rep("orange",10),rep("yellow",11),rep("green",1),rep("blue",7),rep("purple",7))
jj <- cbind(s2016[,1],s2017[,1],s2018[,1],s2019[,1])  # mean
matplot(jj,type="n",xlab='points system',ylab='mean correct places')
points(s2016[,1],col=typecol,pch=1)
points(s2017[,1],col=typecol,pch=2)
points(s2018[,1],col=typecol,pch=3)
points(s2019[,1],col=typecol,pch=4)
legend("topright",lty=0,pch=1:4,legend=c("2016","2017","2018","2019"))
```

```{r,fig=TRUE}
jj <- cbind(s2016[,2],s2017[,2],s2018[,2],s2019[,2])  # prob of winner
matplot(jj,type="n",xlab='points system',ylab='probability of winner correct')
points(s2016[,2],col=typecol,pch=1)
points(s2017[,2],col=typecol,pch=2)
points(s2018[,2],col=typecol,pch=3)
points(s2019[,2],col=typecol,pch=4)
legend("topright",lty=0,pch=1:4,legend=c("2016","2017","2018","2019"))
```

```{r,fig=TRUE}
jj <- cbind(s2016[,3],s2017[,3],s2018[,3],s2019[,3])  # total rank order correct
matplot(jj,type="n",xlab='points system',ylab='probability of total rank order correct')
points(s2016[,3],col=typecol,pch=1)
points(s2017[,3],col=typecol,pch=2)
points(s2018[,3],col=typecol,pch=3)
points(s2019[,3],col=typecol,pch=4)
legend("topright",lty=0,pch=1:4,legend=c("2016","2017","2018","2019"))
```

```{r,makeatable}
table(real_winner_ok=OO[1,]>0,top3_winner_ok=OO[3,]>0)
```
